### 2018-10-16 tex/model.tex
Verision 2.3

The FRQ model can describe a variety of resource scheduling strategies. First, we analyze a naive scheduling strategy. As shown in Figure \ref{fig:model_original}, FRQ model describes a MapReduce job that is fully serially executed. The overlap time between shuffle phase and the reduce phase is \(0\), in which case \(T_{P\_Shuffle}\) is \(0\). Therefore, the overhead of the reduce phase is 0. But since shuffle and computation are serial execution, the total execution time of a job is different from the above:
\begin{equation}
\label{equation_Tjob2}
\begin{aligned}
    T_{Job} &= T_{Map} + T_{Shuffle} + T_{Reduce}
\end{aligned}
\end{equation}
Apache Spark uses this scheduling strategy by default. Due to serialization, the I/O resource is idle during the reduce phase and map phase. The scheduling strategy is simple and has a lot of room for optimization.

Figure \ref{fig:model_hadoop} shows one of the optimization methods. In this scheduling strategy, shuffle phase and reduce phase start at the same time. In this case, \(T_{P\_Shuffle}\) is equal to \(T_{Shuffle}\). Due to the increase in \(T_{P\_Shuffle}\), the time of reduce phase will increase (according to equation \ref{equation_Treduce}). Because the shuffle phase and the computation phase are executed in parallel, the total execution time of job is the sum of \(T_{Map}\) and \(T_{Reduce}\) (see equation \ref{equation_Tjob}). The execution time of shuffle phase is hidden in the reduce phase. This scheduling strategy is used by Hadoop MapReduce. After analyzing this model, we believe that this strategy will be more efficient than the above serial strategy in the same situation. Meanwhile, we found that the I/O resource in the map phase is still idle. This scheduling strategy can be optimized.

@@

\subsection{Model Verification}\label{model_verification}
In order to verify FRQ model, we run experiment on two environments. The first environment is on Amazon EC2 and it has 50 m4.xlarge nodes as shown in Section \ref{stepup}. Another environment is in our lab. Out lab environment has 4 nodes and each nodes has 128GB and 32 CPUs. To simplify the calculation of the FRQ model, we use Hadoop MapReduce as framework and Terasort as experimental application. We deployed Hadoop with SCache and without SCache on both environments.

Table \ref{table1} shows the calculational results of FRQ model in the lab environment. Workload is from 16 GB to 64 GB. \(D\) and \(N\) are set according to the application parameters. \(R, V_{Map}, V_{Shuffle},\)and \(V_{Reduce}\) are calculated based on experimental results. K is the empirical value, we set \(K\) to 0.5 and 0.6, which reflects that \(T_{P\_Shuffle}\) has less impact on the reduce phase in the case of SCache. The formulas of \(T_{Job}, T_{Map}, T_{Reduce}\) and \(T_{Shuffle}\) are Equation \ref{equation_Tjob}, Equation \ref{equation_Tmap}, Equation \ref{equation_Treduce} and Equation \ref{equation_Tshuffle}, respectively. In the case of SCache, Terasort on Hadoop MapReduce satisfies the situation in Figure \ref{fig:model_scache1} (\(V_{Map} \times R \ge V_{Shuffle}\)), thus the formula of \(T_{P\_Shuffle}\) is Equation \ref{equation_Tpshuffle1}. In the case of Legacy, since pre-fetching is not used, \(T_{P\_Shuffle}\) is equal to \(T_{Shuffle}\)(see Equation \ref{equation_Tshuffle}). \(ExpT_{Job}\) represents the actual experiment data, we calculate \(Error\) according to \(T_{Job}\) and \(ExpT_{Job}\). The formula of \(Error\) is:
\begin{equation}
	\label{equation_error}
	\begin{aligned}
		Error &= \frac{ExpT_{Job} - T_{Job}}{T_{Job}}
	\end{aligned}
\end{equation}

@@

In order to verify the above-mentioned two cases when using SCache, we monitor network utilization and plot it in Figure \ref{fig:hadoop_net}. Figure \ref{fig:hadoop_net1} shows the utilization of Terasort in the lab environment. The network utilization remains high until shuffle phase is complete. This situation is consistent with Figure \ref{fig:model_scache1}. Figure \ref{fig:hadoop_net2} shows the utilization in Amazon EC2 environment. 
The network utilization has 5 regular peaks. This situation is also consistent with Figure \ref{fig:model_scache2}. Therefore, we believe that FRQ model is able to accurately describe framework with SCache.

>>>>

The FRQ model can describe a variety of resource scheduling strategies. First, we analyze a naive scheduling strategy. As shown in Figure \ref{fig:model_original}, FRQ model describes a MapReduce job that is fully serially executed. The overlap time between the shuffle phase and the reduce phase is \(0\), in which case \(T_{P\_Shuffle}\) is \(0\). Therefore, the overhead of the reduce phase is 0. But since shuffle and computation are serial execution, the total execution time of a job is different from the above:
\begin{equation}
\label{equation_Tjob2}
\begin{aligned}
    T_{Job} &= T_{Map} + T_{Shuffle} + T_{Reduce}
\end{aligned}
\end{equation}
Apache Spark uses this scheduling strategy by default. Due to serialization, the I/O resource is idle during the reduce phase and map phase. The scheduling strategy is simple and has a lot of room for optimization.

Figure \ref{fig:model_hadoop} shows one of the optimization methods. In this scheduling strategy, shuffle phase and reduce phase start at the same time. In this case, \(T_{P\_Shuffle}\) is equal to \(T_{Shuffle}\). Due to the increase in \(T_{P\_Shuffle}\), the time of reduce phase will increase (according to equation \ref{equation_Treduce}). Because the shuffle phase and the computation phase are executed in parallel, the total execution time of a job is the sum of \(T_{Map}\) and \(T_{Reduce}\) (see equation \ref{equation_Tjob}). The execution time of the shuffle phase is hidden in the reduce phase. This scheduling strategy is used by Hadoop MapReduce. After analyzing this model, we believe that this strategy will be more efficient than the above serial strategy in the same situation. Meanwhile, we found that the I/O resource in the map phase is still idle. This scheduling strategy can be optimized.

@@

\subsection{Model Verification}\label{model_verification}
In order to verify FRQ model, we run experiments on two environments. The first environment is on Amazon EC2 and it has 50 m4.xlarge nodes as shown in Section \ref{stepup}. Another environment is in our lab. Our in-house environment has 4 nodes and each node has 128GB and 32 CPUs. To simplify the calculation of the FRQ model, we use Hadoop MapReduce as a framework and use Terasort as a experimental application. We deployed Hadoop with SCache and without SCache in both environments.

Table \ref{table1} shows the calculational results of FRQ model in the in-house environment. Workload is from 16 GB to 64 GB. \(D\) and \(N\) are set according to the application parameters. \(R, V_{Map}, V_{Shuffle},\)and \(V_{Reduce}\) are calculated based on experimental results. K is the empirical value, we set \(K\) to 0.5 and 0.6, which reflects that \(T_{P\_Shuffle}\) has less impact on the reduce phase in the case of SCache. The formulas of \(T_{Job}, T_{Map}, T_{Reduce}\) and \(T_{Shuffle}\) are Equation \ref{equation_Tjob}, Equation \ref{equation_Tmap}, Equation \ref{equation_Treduce} and Equation \ref{equation_Tshuffle}, respectively. In the case of SCache, Terasort on Hadoop MapReduce satisfies the situation in Figure \ref{fig:model_scache1} (\(V_{Map} \times R \ge V_{Shuffle}\)), thus the formula of \(T_{P\_Shuffle}\) is Equation \ref{equation_Tpshuffle1}. In the case of Legacy, since pre-fetching is not used, \(T_{P\_Shuffle}\) is equal to \(T_{Shuffle}\)(see Equation \ref{equation_Tshuffle}). \(ExpT_{Job}\) represents the actual experiment data, we calculate \(Error\) according to \(T_{Job}\) and \(ExpT_{Job}\). The formula of \(Error\) is:
\begin{equation}
	\label{equation_error}
	\begin{aligned}
		Error &= \frac{ExpT_{Job} - T_{Job}}{T_{Job}}
	\end{aligned}
\end{equation}

@@

In order to verify the above-mentioned two cases when using SCache, we monitor network utilization and plot it in Figure \ref{fig:hadoop_net}. Figure \ref{fig:hadoop_net1} shows the utilization of Terasort in the in-house environment. The network utilization remains high until shuffle phase is complete. This situation is consistent with Figure \ref{fig:model_scache1}. Figure \ref{fig:hadoop_net2} shows the utilization in Amazon EC2 environment. 
The network utilization has 5 regular peaks. This situation is also consistent with Figure \ref{fig:model_scache2}. Therefore, we believe that FRQ model is able to accurately describe the performance of a framework with SCache.

### 2018-10-16 tex/optimization.tex
Version 2.2
Verision 2.3

For the most DAG applications with random large scale input, 
the $BlockSize_{ji}$ in a particular shuffle can be predicted with decent accuracy by liner regression model (i.e., equation \ref{linearregresion}) based on observation that the ratio of map output size and input size are invariant given the same job configuration \cite{ishuffle, predict}: 
\begin{equation}
\label{linearregresion}
\begin{aligned}
	BlockSize_{ji} = a \times inputSize_j + b
\end{aligned}
\end{equation}
The $inputSize_j$ is the input size of $j$th map task. 
The $a$ and $b$ can be determined using the observed $inputSize_j$ and $BlockSize_{ji}$.

@@

\noindent
\begin{minipage}{0.95\columnwidth}
\begin{algorithm}[H]
\caption{Accumulated Heuristic Scheduling for Multi-Shuffles}
\label{mhminheap}
	\begin{algorithmic}[1]
	\small
	\Procedure{\Large m\_schedule}{$m, host\_id, p\_reduces, \text{\emph{shuffles}}$}
		\State $m\gets$ partition number of map tasks
		\Comment \emph{shuffles} is the previous schedule result 
		\ForAll{$r$ in $p\_reduces$}
			\State $r.size \mathrel{+}= \text{\emph{shuffles}}\left[r.rid\right].size$
			\State $new\_prob\gets \text{\emph{shuffles}}\left[r.rid\right].size / r.size$
			\If{$new\_prob\geq r.prob$}
				\State $r.prob\gets new\_prob$
				\State $r.host\_id\gets \text{\emph{shuffles}}\left[r.rid\right].assigned\_host$
			\EndIf
		\EndFor
		\State $M\gets$ $SCHEDULE\left(m, host\_id, p\_reduces\right)$
		\ForAll{$host\_id$ in $M$}
			\Comment Re-shuffle
			\ForAll{$r$ in $M\left[host\_id\right].reduces$}
				\If{$host\neq \text{\emph{shuffles}}\left[r.rid\right].assigned\_host$}
				\State Re-shuffle data to $host$
				\State $\text{\emph{shuffles}}\left[r.rid\right].assigned\_host\gets host$
				\EndIf
			\EndFor
		\EndFor
		\Return $M$
	\EndProcedure
	\end{algorithmic}
\end{algorithm}
\end{minipage}
\subsubsection{Cope with Multiple Shuffle Dependencies}
% \ifrevision
% \marginpar{E5}
% \fi
A reduce stage can have more than one shuffle dependencies in the current DAG computing frameworks. 
The technique mentioned in Section \ref{shuffleprediction} can only handle an ongoing shuffle. 
For those pending shuffles, it is impossible to predict their sizes. 
This problem can be solved by having all map tasks of pending shuffles launched simultaneously. 
But doing this introduces large overhead such as extra task serialization. 
To avoid violating the optimization from framework, we present the Accumulated Heuristic Scheduling algorithm to cope with multiple shuffle dependencies.

>>>>

For the most DAG applications with random large scale input, 
the $BlockSize_{ji}$ in a particular shuffle can be predicted with decent accuracy by liner regression model (i.e., equation \ref{linearregresion}) based on observation that the ratio of map output size and input size are invariant given the same job configuration \cite{guo2017ishuffle, predict}: 
\begin{equation}
\label{linearregresion}
\begin{aligned}
	BlockSize_{ji} = a \times inputSize_j + b
\end{aligned}
\end{equation}
The $inputSize_j$ is the input size of $j$th map task. 
The $a$ and $b$ can be determined using the observed $inputSize_j$ and $BlockSize_{ji}$.

@@

\noindent
\begin{minipage}{0.95\columnwidth}
\begin{algorithm}[H]
\caption{Accumulated Heuristic Scheduling for Multi-Shuffles}
\label{mhminheap}
	\begin{algorithmic}[1]
	\small
	\Procedure{\Large m\_schedule}{$m, host\_id, p\_reduces, \text{\emph{shuffles}}$}
		\State $m\gets$ partition number of map tasks
		\Comment \emph{shuffles} are the previous schedule result 
		\ForAll{$r$ in $p\_reduces$}
			\State $r.size \mathrel{+}= \text{\emph{shuffles}}\left[r.rid\right].size$
			\State $new\_prob\gets \text{\emph{shuffles}}\left[r.rid\right].size / r.size$
			\If{$new\_prob\geq r.prob$}
				\State $r.prob\gets new\_prob$
				\State $r.host\_id\gets \text{\emph{shuffles}}\left[r.rid\right].assigned\_host$
			\EndIf
		\EndFor
		\State $M\gets$ $SCHEDULE\left(m, host\_id, p\_reduces\right)$
		\ForAll{$host\_id$ in $M$}
			\Comment Re-shuffle
			\ForAll{$r$ in $M\left[host\_id\right].reduces$}
				\If{$host\neq \text{\emph{shuffles}}\left[r.rid\right].assigned\_host$}
				\State Re-shuffle data to $host$
				\State $\text{\emph{shuffles}}\left[r.rid\right].assigned\_host\gets host$
				\EndIf
			\EndFor
		\EndFor
		\Return $M$
	\EndProcedure
	\end{algorithmic}
\end{algorithm}
\end{minipage}
\subsubsection{Cope with Multiple Shuffle Dependencies}
% \ifrevision
% \marginpar{E5}
% \fi
A reduce stage can have more than one shuffle dependencies in the current DAG computing frameworks. 
The technique mentioned in Section \ref{shuffleprediction} can only handle an ongoing shuffle. 
For those pending shuffles, it is impossible to predict their sizes. 
This problem can be solved by having all map tasks of pending shuffles launched simultaneously. 
But doing this introduces large overhead such as extra task serialization. 
To avoid violating the optimization from framework, we present the Accumulated Heuristic Scheduling algorithm to cope with multiple shuffle dependencies.

### 2018-10-16 tex/relatedwork.tex
fzw revision
Verision 2.3

{\color{blue}
\textbf{Modeling}: Most well-known DAG computing frameworks use similar \textit{Bulk Synchronize Parallel} (BSP)\cite{valiant1990bridging} model to control data synchronization in each computing phase, i.e. \textit{stage} in Spark, \textit{superstep} in Pregel\cite{malewicz2010pregel} and so on (Apache Hadoop Madpreduce\footnote{http://hadoop.apache.com/} can also be considered as a special case of only one superstep in BSP model). 
In the process of optimizing the shuffle phases between adjacent computing phases, we design a performance model to assist in analyzing computing process.
Inspired by \cite{verma2011aria}, \cite{herodotou2011hadoop}, and \cite{polo2010performance}, we present \textit{Framework Resources Quantification} (FRQ) model to describe the performance of DAG frameworks.
In \cite{verma2011aria}, the author designs a model and divides execution into three parts: Map, Shuffle and Reduce. And then the author uses a greedy algorithm to roughly calculate the max, min and mean execution time of Map and Reduce phases.
In \cite{herodotou2011hadoop}, the author presents a detailed set of mathematical performance models for describing the execution of a MapReduce job. The execution is separated into the phases: Read, Map, Collect, Spill, Merge, Shuffle, Merge, and Reduce. The performance models describe each above-mentioned phases and combine into a overall MapReduce job model. 
However, none of the above models meet our requirements for analyzing shuffle.
The model in \cite{verma2011aria} is not able to accurately describe the overhead caused by shuffle under different scheduling strategies. The model in \cite{herodotou2011hadoop} calculates overhead of various phases including shuffle, but most of them are redundant. 
Different from these models, our FRQ model quantifies computing and I/O resources and displays them in time dimension. FRQ model focuses on describing the overhead caused by shuffle in different scheduling strategies, which satisfy our demand.
}

\textbf{Pre-scheduling}: Slow-start from Apache Hadoop MapReduce is a classic approach to handle shuffle overhead. 
Starfish \cite{starfish} gets sampled data statics for self-tuning system parameters (e.g. slow-start, etc). 
DynMR \cite{dynmr} dynamically starts reduce tasks in late map stage. 
All of them have the explicit I/O time in occupied slots. 
SCache instead starts shuffle pre-fetching without consuming slots. 
iShuffle \cite{ishuffle} decouples shuffle from reducers and designs a centralized shuffle controller. 
But it can neither handle multiple shuffles nor schedule multiple rounds of reduce tasks. 
iHadoop \cite{ihadoop} aggressively pre-schedules tasks in multiple successive stages to start fetching shuffle. 
But we have proved that randomly assign tasks may hurt the overall performance in Section \ref{randomassign}. 
Different from these works, SCache pre-schedules multiple shuffles without breaking load balancing.

%  by combining DAG information and heuristic algorithms.
\textbf{Delay-scheduling}: Delay Scheduling \cite{delay} delays tasks assignment to get better data locality, which can reduce the network traffic. 
ShuffleWatcher \cite{shufflewatcher} delays shuffle fetching when network is saturated. 
At the same time, it achieves better data locality. 
Both Quincy \cite{quincy} and Fair Scheduling \cite{preemptive} can reduce shuffle data by optimizing data locality of map tasks. 
But all of them cannot mitigate explicit I/O in both map and reduce tasks. 
In addition, their optimizations fluctuate under different network performances and data distributions, whereas SCache can provide a stable performance gain by shuffle data pre-fetching and in-memory caching.

>>>>

{\color{blue}
\textbf{Modeling}: Most representative DAG computing frameworks use similar \textit{Bulk Synchronize Parallel} (BSP)\cite{valiant1990bridging} model to control data synchronization in each computing phase, i.e. \textit{stage} in Spark, \textit{superstep} in Pregel\cite{malewicz2010pregel} and so on (Apache Hadoop MapReduce\footnote{http://hadoop.apache.com/} can also be considered as a special case of only one superstep in BSP model). 
In the process of optimizing the shuffle phases between adjacent computing phases, we design a performance model to assist in analyzing computing process.
There are also lots of performance models for MapReduce have been proposed, such as \cite{verma2011aria, khan2016hadoop, herodotou2011hadoop, chen2014cresp}.
Verma et al. \cite{verma2011aria} proposed the ARIA model to estimate the required resources based on the job information, the amount of input data and a specified soft deadline.
Khan et al. \cite{khan2016hadoop} proposed the HP model which extends the ARIA model. The HP model adds scaling factors and uses a simple linear regression to estimate the job execution time on larger datasets.
In \cite{herodotou2011hadoop}, Herodotou proposed a detailed set of mathematical performance models for describing the execution of a MapReduce job. The execution is separated into the phases: Read, Map, Collect, Spill, Merge, Shuffle, Merge, and Reduce. The set of performance models describe each above-mentioned phases and combine into an overall MapReduce job model. 
Chen et al. \cite{chen2014cresp} proposed the CRESP model which is a cost model that estimates the performance of a job then 
provisions the resources for the job.

However, the above models are not able to accurately describe the overhead caused by the shuffle process under different scheduling strategies. 
Different from these models, our FRQ model quantifies computing and I/O resources and displays them in the time dimension. FRQ model focuses on describing the overhead caused by the shuffle process in different scheduling strategies, which satisfy our demand.
}

\textbf{Pre-scheduling}: Slow-start from Apache Hadoop MapReduce is a classic approach to handle shuffle overhead. 
Starfish \cite{starfish} gets sampled data statics for self-tuning system parameters (e.g. slow-start, etc). 
DynMR \cite{dynmr} dynamically starts reduce tasks in late map stage. 
All of them have the explicit I/O time in occupied slots. 
SCache instead starts shuffle pre-fetching without consuming slots. 
iShuffle \cite{guo2017ishuffle} decouples shuffle from reducers and designs a centralized shuffle controller. 
But it can neither handle multiple shuffles nor schedule multiple rounds of reduce tasks. 
iHadoop \cite{ihadoop} aggressively pre-schedules tasks in multiple successive stages to start fetching shuffle. 
But we have proved that randomly assign tasks may hurt the overall performance in Section \ref{randomassign}. 
Different from these works, SCache pre-schedules multiple shuffles without breaking load balancing.

%  by combining DAG information and heuristic algorithms.
\textbf{Delay-scheduling}: Delay Scheduling \cite{delay} delays tasks assignment to get better data locality, which can reduce the network traffic. 
ShuffleWatcher \cite{shufflewatcher} delays shuffle fetching when the network is saturated. 
At the same time, it achieves better data locality. 
Both Quincy \cite{quincy} and Fair Scheduling \cite{preemptive} can reduce shuffle data by optimizing data locality of map tasks. 
But all of them cannot mitigate explicit I/O in both map and reduce tasks. 
In addition, their optimizations fluctuate under different network performances and data distributions, whereas SCache can provide a stable performance gain by shuffle data pre-fetching and in-memory caching.
